The role of aneuploidy in the evolution of cancer drug resistance

### 2023-07-25 EvolutionaryRescue1.tex
beneficial...

\begin{table}
\begin{center}
  \begin{tabular}{| l |p{5cm}| c | c | p{3cm} |}
    \hline
     & Name & Value & Units & References \\ \hline
    $N$ & Initial tumor size & $10^7-10^9$ & cells  & \citet{del2009does} \\ \hline
    $\lambda_w$ & Wildtype division rate& 0.14 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\mu_w$ & Wildtype death rate& 0.17 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\lambda_a$  & Aneuploid division rate$^\ast$ & 0.14 & 1/days  & - \\ \hline
    $\mu_a$ & Aneuploid death rate$^\ast$ & $0.13-0.17$ & 1/days  & - \\ \hline
    $\lambda_m$ & Mutant division rate& 0.14 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\mu_m$ & Mutant death rate& 0.13 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $u$ & Missegregation rate& $10^{-3}-10^{-2}$ & 1$\slash$cell division  & \citet{nowak2004evolutionary,bakker2023predicting} \\ \hline
    $v$ & Mutation rate& $10^{-7}-10^{-9}$ &  1$\slash$gene$\slash$cell division  & \citet{nowak2004evolutionary} \\ 
    % TODO citing Nowak 2004 for the rates is strange because it is a theory paper - cite the original empirical papers
    \hline
  \end{tabular}
\caption{\textbf{Model parameters.} NEED DIFFERENT REFS---THESE ARE MOSTLY THEORY PAPERS. CHECK BIONUMBERS?
Aneuploid birth rate $\lambda_a$ is set to the same value as the wildtype and mutant birth rates, $\lambda_w$ and $\lambda_m$.
Aneuploid death rate $\mu_a$ is set to an intermediate value between the wildtype and mutant death rates, $\mu_w$ and $\mu_m$.}
  \label{table1}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
  \begin{tabular}{| l |p{5cm}| c | c | p{3cm} |}
    \hline
     & Name & Value & Units & References \\ \hline
    $N$ & Initial tumor size & $10^7-10^9$ & cells  & \citet{del2009does} \\ \hline
    $\lambda_w$ & Wildtype division rate& 0.14 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\mu_w$ & Wildtype death rate& 0.17 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\lambda_a$  & Aneuploid division rate$^\ast$ & 0.14 & 1/days  & - \\ \hline
    $\mu_a$ & Aneuploid death rate$^\ast$ & $0.13-0.17$ & 1/days  & - \\ \hline
    $\lambda_m$ & Mutant division rate& 0.14 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $\mu_m$ & Mutant death rate& 0.13 & 1/days  & \citet{bozic2013evolutionary} \\ \hline
    $u$ & Beneficial aneuploidy rate& $10^{-3}-10^{-2}$ & 1 / chromosome / cell division  & \citet{nowak2004evolutionary,bakker2023predicting} \\ \hline
    $v$ & Beneficial mutation rate& $10^{-7}-10^{-9}$ &  1 / gene / cell division  & \citet{nowak2004evolutionary} \\ 
    % TODO citing Nowak 2004 for the rates is strange because it is a theory paper - cite the original empirical papers
    % TODO resistance and aneuploidy could increase lambda, not just reduce mu.
    \hline
  \end{tabular}
\caption{\textbf{Model parameters.} NEED DIFFERENT REFS---THESE ARE MOSTLY THEORY PAPERS. CHECK BIONUMBERS?
Aneuploid birth rate $\lambda_a$ is set to the same value as the wildtype and mutant birth rates, $\lambda_w$ and $\lambda_m$.
Aneuploid death rate $\mu_a$ is set to an intermediate value between the wildtype and mutant death rates, $\mu_w$ and $\mu_m$.}
  \label{table1}
\end{center}
\end{table}
